Language learning in context via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
tweak fig. 2 caption

\begin{SCfigure}
\centering
\includegraphics[width=0.5\textwidth]{figures/horn-composite.pdf}
% \includegraphics[width=0.48\textwidth]{figures/horn-emergence-1.pdf}
\caption{\label{fig:horn} Example simulations showing the
  lexicalization of Horn implicatures. Plotting conventions are as
  above. In the first run, speaker and listener converge on a sparse
  and  efficient communicative equilibrium, while in the second they reach
  a sub-optimal equilibrium.}
\end{SCfigure}

>>>>

\begin{SCfigure}
\centering
\includegraphics[width=0.5\textwidth]{figures/horn-composite.pdf}
% \includegraphics[width=0.48\textwidth]{figures/horn-emergence-1.pdf}
\caption{\label{fig:horn} Example simulations showing the
  lexicalization of Horn implicatures. Plotting conventions are as
  above. In the first run, speaker and listener converge on a sparse
  and  efficient communicative equilibrium, in which ``cheap'' means
  \textsc{COMMON} and ``expensive'' means \textsc{RARE}, while in the
  second they reach a sub-optimal equilibrium. As shown in
  Fig.~\ref{fig:emergence-average}, the former is more typical.}
\end{SCfigure}
